Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-28 journal/article.tex
T: Change leaders: Edit

A significant change effort requires entities in the organization who take
leadership in the change. Getting a large group of people aligned towards a
common goal, in many cases a completely new way of working, requires that
someone takes charge for the undertaking.

Change was lead in X ways.

Leadership for change showed on all organizational levels.
% The ways how change was lead was similar on each level.

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        Change leaders         &  Described in  \\
        \midrule
        High-up change leaders or sponsors  &
                P3, P5, P24, P31, P36, P38, P46, P49  \\
        Change leaders on other organizational levels  &
                P2, P6, P9, P14, P17, P18, P27  \\
        Agile task group for coordinating change   &
                P4, P16, P18, P21, P23, P25, P30, P40, P41,
                P43, P45, P48, P49, P50  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of entities leading change in the agile transformation}
    \label{table:transformation_leadership}
\end{table}

@@

>>>>

A significant change effort requires entities in the organization who take
leadership in the change. Getting a large group of people aligned towards a
common goal, in many cases a completely new way of working, requires that
someone takes charge for the undertaking. The primary sources showed evidence of
leadership for change on all organizational levels. Table
\ref{table:transformation_leadership} summarizes different types of change
leaders that were discovered.

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        Change leaders         &  Described in  \\
        \midrule
        High-up change leaders or sponsors  &
                P3, P5, P24, P31, P36, P38, P46, P49  \\
        Agile task group for coordinating change   &
                P4, P16, P18, P21, P23, P25, P30, P40, P41,
                P43, P45, P48, P49, P50  \\
        Change leaders on other organizational levels  &
                P2, P6, P9, P14, P17, P18, P27  \\
        Informal spreading of agile awareness  &
                P3, P6, P40  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of entities leading change in the agile transformation}
    \label{table:transformation_leadership}
\end{table}

@@

% Informal spreading of awareness

Change leadership showed on the lowest level as informal spreading of awareness
of agile methods.
Benefield [P6] describes that the strongest force over other change leaders was
letting agile knowledge spread virally. New Scrum teams were emerging as people
heard of the new methodology [P6].
It was similarly described that in an organization with an introverted culture
the proclamations of managers could not match with the power of practitioners
explaining to others how they had succeeded in with the agile method [P40].
Even casual hallway talks could spread the word effectively, and it was
also easier to encounter people from other parts of the organization in an
informal context [P3].
